Estimating survival in left filtered data

### 2021-12-11 reports/resources/results.tex
Interim results; running on GM data now

% Created by tikzDevice version 0.12.3.1 on 2021-12-09 11:35:50
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.29) --
	( 70.24,532.29) --
	( 70.24,532.07) --
	( 83.42,532.07) --
	( 83.42,531.75) --
	( 96.59,531.75) --
	( 96.59,531.34) --
	(109.77,531.34) --
	(109.77,530.83) --
	(122.95,530.83) --
	(122.95,530.24) --
	(136.12,530.24) --
	(136.12,529.56) --
	(149.30,529.56) --
	(149.30,528.80) --
	(162.48,528.80) --
	(162.48,527.94) --
	(175.66,527.94) --
	(175.66,526.99) --
	(188.83,526.99) --
	(188.83,525.97) --
	(202.01,525.97) --
	(202.01,524.86) --
	(215.19,524.86) --
	(215.19,523.67) --
	(228.36,523.67) --
	(228.36,522.42) --
	(241.54,522.42) --
	(241.54,521.08) --
	(254.72,521.08) --
	(254.72,519.67) --
	(267.89,519.67) --
	(267.89,518.18) --
	(281.07,518.18) --
	(281.07,516.64) --
	(294.25,516.64) --
	(294.25,515.02);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.22) --
	( 70.24,532.22) --
	( 70.24,531.89) --
	( 83.42,531.89) --
	( 83.42,531.43) --
	( 96.59,531.43) --
	( 96.59,530.86) --
	(109.77,530.86) --
	(109.77,530.19) --
	(122.95,530.19) --
	(122.95,529.41) --
	(136.12,529.41) --
	(136.12,528.53) --
	(149.30,528.53) --
	(149.30,527.54) --
	(162.48,527.54) --
	(162.48,526.46) --
	(175.66,526.46) --
	(175.66,525.27) --
	(188.83,525.27) --
	(188.83,523.99) --
	(202.01,523.99) --
	(202.01,522.62) --
	(215.19,522.62) --
	(215.19,521.16) --
	(228.36,521.16) --
	(228.36,519.61) --
	(241.54,519.61) --
	(241.54,517.96) --
	(254.72,517.96) --
	(254.72,516.23) --
	(267.89,516.23) --
	(267.89,514.43) --
	(281.07,514.43) --
	(281.07,512.53) --
	(294.25,512.53) --
	(294.25,510.60);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,531.49) --
	( 70.24,531.49) --
	( 70.24,530.36) --
	( 83.42,530.36) --
	( 83.42,529.08) --
	( 96.59,529.08) --
	( 96.59,527.72) --
	(109.77,527.72) --
	(109.77,526.29) --
	(122.95,526.29) --
	(122.95,524.82) --
	(136.12,524.82) --
	(136.12,523.34) --
	(149.30,523.34) --
	(149.30,521.83) --
	(162.48,521.83) --
	(162.48,520.30) --
	(175.66,520.30) --
	(175.66,518.75) --
	(188.83,518.75) --
	(188.83,517.21) --
	(202.01,517.21) --
	(202.01,515.66) --
	(215.19,515.66) --
	(215.19,514.12) --
	(228.36,514.12) --
	(228.36,512.61) --
	(241.54,512.61) --
	(241.54,511.09) --
	(254.72,511.09) --
	(254.72,509.58) --
	(267.89,509.58) --
	(267.89,508.07) --
	(281.07,508.07) --
	(281.07,506.59) --
	(294.25,506.59) --
	(294.25,505.04);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,530.98) --
	( 70.24,530.98) --
	( 70.24,529.33) --
	( 83.42,529.33) --
	( 83.42,527.51) --
	( 96.59,527.51) --
	( 96.59,525.64) --
	(109.77,525.64) --
	(109.77,523.73) --
	(122.95,523.73) --
	(122.95,521.81) --
	(136.12,521.81) --
	(136.12,519.88) --
	(149.30,519.88) --
	(149.30,517.95) --
	(162.48,517.95) --
	(162.48,516.03) --
	(175.66,516.03) --
	(175.66,514.10) --
	(188.83,514.10) --
	(188.83,512.19) --
	(202.01,512.19) --
	(202.01,510.32) --
	(215.19,510.32) --
	(215.19,508.45) --
	(228.36,508.45) --
	(228.36,506.59) --
	(241.54,506.59) --
	(241.54,504.74) --
	(254.72,504.74) --
	(254.72,502.91) --
	(267.89,502.91) --
	(267.89,501.12) --
	(281.07,501.12) --
	(281.07,499.32) --
	(294.25,499.32) --
	(294.25,497.50);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.82) --
	( 70.24,436.82) --
	( 70.24,436.59) --
	( 83.42,436.59) --
	( 83.42,436.27) --
	( 96.59,436.27) --
	( 96.59,435.85) --
	(109.77,435.85) --
	(109.77,435.33) --
	(122.95,435.33) --
	(122.95,434.71) --
	(136.12,434.71) --
	(136.12,434.01) --
	(149.30,434.01) --
	(149.30,433.22) --
	(162.48,433.22) --
	(162.48,432.34) --
	(175.66,432.34) --
	(175.66,431.35) --
	(188.83,431.35) --
	(188.83,430.30) --
	(202.01,430.30) --
	(202.01,429.17) --
	(215.19,429.17) --
	(215.19,427.94) --
	(228.36,427.94) --
	(228.36,426.65) --
	(241.54,426.65) --
	(241.54,425.29) --
	(254.72,425.29) --
	(254.72,423.84) --
	(267.89,423.84) --
	(267.89,422.32) --
	(281.07,422.32) --
	(281.07,420.74) --
	(294.25,420.74) --
	(294.25,419.11);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.75) --
	( 70.24,436.75) --
	( 70.24,436.42) --
	( 83.42,436.42) --
	( 83.42,435.95) --
	( 96.59,435.95) --
	( 96.59,435.37) --
	(109.77,435.37) --
	(109.77,434.66) --
	(122.95,434.66) --
	(122.95,433.84) --
	(136.12,433.84) --
	(136.12,432.91) --
	(149.30,432.91) --
	(149.30,431.87) --
	(162.48,431.87) --
	(162.48,430.71) --
	(175.66,430.71) --
	(175.66,429.46) --
	(188.83,429.46) --
	(188.83,428.14) --
	(202.01,428.14) --
	(202.01,426.71) --
	(215.19,426.71) --
	(215.19,425.22) --
	(228.36,425.22) --
	(228.36,423.62) --
	(241.54,423.62) --
	(241.54,421.93) --
	(254.72,421.93) --
	(254.72,420.17) --
	(267.89,420.17) --
	(267.89,418.34) --
	(281.07,418.34) --
	(281.07,416.45) --
	(294.25,416.45) --
	(294.25,414.50);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.03) --
	( 70.24,436.03) --
	( 70.24,434.87) --
	( 83.42,434.87) --
	( 83.42,433.58) --
	( 96.59,433.58) --
	( 96.59,432.19) --
	(109.77,432.19) --
	(109.77,430.73) --
	(122.95,430.73) --
	(122.95,429.20) --
	(136.12,429.20) --
	(136.12,427.66) --
	(149.30,427.66) --
	(149.30,426.11) --
	(162.48,426.11) --
	(162.48,424.55) --
	(175.66,424.55) --
	(175.66,422.95) --
	(188.83,422.95) --
	(188.83,421.38) --
	(202.01,421.38) --
	(202.01,419.81) --
	(215.19,419.81) --
	(215.19,418.23) --
	(228.36,418.23) --
	(228.36,416.67) --
	(241.54,416.67) --
	(241.54,415.13) --
	(254.72,415.13) --
	(254.72,413.59) --
	(267.89,413.59) --
	(267.89,412.05) --
	(281.07,412.05) --
	(281.07,410.53) --
	(294.25,410.53) --
	(294.25,408.97);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,435.55) --
	( 70.24,435.55) --
	( 70.24,433.88) --
	( 83.42,433.88) --
	( 83.42,432.04) --
	( 96.59,432.04) --
	( 96.59,430.10) --
	(109.77,430.10) --
	(109.77,428.11) --
	(122.95,428.11) --
	(122.95,426.11) --
	(136.12,426.11) --
	(136.12,424.08) --
	(149.30,424.08) --
	(149.30,422.06) --
	(162.48,422.06) --
	(162.48,420.03) --
	(175.66,420.03) --
	(175.66,418.03) --
	(188.83,418.03) --
	(188.83,416.08) --
	(202.01,416.08) --
	(202.01,414.13) --
	(215.19,414.13) --
	(215.19,412.24) --
	(228.36,412.24) --
	(228.36,410.33) --
	(241.54,410.33) --
	(241.54,408.44) --
	(254.72,408.44) --
	(254.72,406.60) --
	(267.89,406.60) --
	(267.89,404.77) --
	(281.07,404.77) --
	(281.07,402.99) --
	(294.25,402.99) --
	(294.25,401.13);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.35) --
	( 70.24,341.35) --
	( 70.24,341.12) --
	( 83.42,341.12) --
	( 83.42,340.81) --
	( 96.59,340.81) --
	( 96.59,340.40) --
	(109.77,340.40) --
	(109.77,339.90) --
	(122.95,339.90) --
	(122.95,339.31) --
	(136.12,339.31) --
	(136.12,338.63) --
	(149.30,338.63) --
	(149.30,337.87) --
	(162.48,337.87) --
	(162.48,337.01) --
	(175.66,337.01) --
	(175.66,336.06) --
	(188.83,336.06) --
	(188.83,335.04) --
	(202.01,335.04) --
	(202.01,333.93) --
	(215.19,333.93) --
	(215.19,332.74) --
	(228.36,332.74) --
	(228.36,331.49) --
	(241.54,331.49) --
	(241.54,330.15) --
	(254.72,330.15) --
	(254.72,328.74) --
	(267.89,328.74) --
	(267.89,327.25) --
	(281.07,327.25) --
	(281.07,325.71) --
	(294.25,325.71) --
	(294.25,324.10);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.27) --
	( 70.24,341.27) --
	( 70.24,340.93) --
	( 83.42,340.93) --
	( 83.42,340.46) --
	( 96.59,340.46) --
	( 96.59,339.87) --
	(109.77,339.87) --
	(109.77,339.17) --
	(122.95,339.17) --
	(122.95,338.37) --
	(136.12,338.37) --
	(136.12,337.47) --
	(149.30,337.47) --
	(149.30,336.45) --
	(162.48,336.45) --
	(162.48,335.35) --
	(175.66,335.35) --
	(175.66,334.13) --
	(188.83,334.13) --
	(188.83,332.82) --
	(202.01,332.82) --
	(202.01,331.40) --
	(215.19,331.40) --
	(215.19,329.89) --
	(228.36,329.89) --
	(228.36,328.30) --
	(241.54,328.30) --
	(241.54,326.62) --
	(254.72,326.62) --
	(254.72,324.85) --
	(267.89,324.85) --
	(267.89,323.00) --
	(281.07,323.00) --
	(281.07,321.08) --
	(294.25,321.08) --
	(294.25,319.07);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,340.55) --
	( 70.24,340.55) --
	( 70.24,339.41) --
	( 83.42,339.41) --
	( 83.42,338.15) --
	( 96.59,338.15) --
	( 96.59,336.79) --
	(109.77,336.79) --
	(109.77,335.37) --
	(122.95,335.37) --
	(122.95,333.90) --
	(136.12,333.90) --
	(136.12,332.42) --
	(149.30,332.42) --
	(149.30,330.91) --
	(162.48,330.91) --
	(162.48,329.38) --
	(175.66,329.38) --
	(175.66,327.83) --
	(188.83,327.83) --
	(188.83,326.29) --
	(202.01,326.29) --
	(202.01,324.76) --
	(215.19,324.76) --
	(215.19,323.21) --
	(228.36,323.21) --
	(228.36,321.70) --
	(241.54,321.70) --
	(241.54,320.17) --
	(254.72,320.17) --
	(254.72,318.66) --
	(267.89,318.66) --
	(267.89,317.16) --
	(281.07,317.16) --
	(281.07,315.68) --
	(294.25,315.68) --
	(294.25,314.13);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,340.03) --
	( 70.24,340.03) --
	( 70.24,338.32) --
	( 83.42,338.32) --
	( 83.42,336.45) --
	( 96.59,336.45) --
	( 96.59,334.51) --
	(109.77,334.51) --
	(109.77,332.52) --
	(122.95,332.52) --
	(122.95,330.54) --
	(136.12,330.54) --
	(136.12,328.59) --
	(149.30,328.59) --
	(149.30,326.59) --
	(162.48,326.59) --
	(162.48,324.64) --
	(175.66,324.64) --
	(175.66,322.66) --
	(188.83,322.66) --
	(188.83,320.72) --
	(202.01,320.72) --
	(202.01,318.76) --
	(215.19,318.76) --
	(215.19,316.84) --
	(228.36,316.84) --
	(228.36,314.94) --
	(241.54,314.94) --
	(241.54,313.05) --
	(254.72,313.05) --
	(254.72,311.18) --
	(267.89,311.18) --
	(267.89,309.34) --
	(281.07,309.34) --
	(281.07,307.52) --
	(294.25,307.52) --
	(294.25,305.63);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,245.72) --
	( 70.24,245.72) --
	( 70.24,245.20) --
	( 83.42,245.20) --
	( 83.42,244.44) --
	( 96.59,244.44) --
	( 96.59,243.50) --
	(109.77,243.50) --
	(109.77,242.30) --
	(122.95,242.30) --
	(122.95,240.95) --
	(136.12,240.95) --
	(136.12,239.38) --
	(149.30,239.38) --
	(149.30,237.62) --
	(162.48,237.62) --
	(162.48,235.68) --
	(175.66,235.68) --
	(175.66,233.51) --
	(188.83,233.51) --
	(188.83,231.15) --
	(202.01,231.15) --
	(202.01,228.63) --
	(215.19,228.63) --
	(215.19,225.94) --
	(228.36,225.94) --
	(228.36,223.15) --
	(241.54,223.15) --
	(241.54,220.21) --
	(254.72,220.21) --
	(254.72,217.04) --
	(267.89,217.04) --
	(267.89,213.83) --
	(281.07,213.83) --
	(281.07,210.42) --
	(294.25,210.42) --
	(294.25,206.83);
\definecolor{drawColor}{RGB}{0,191,196}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-12-10 17:23:19
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.30) --
	( 70.24,532.30) --
	( 70.24,532.07) --
	( 83.42,532.07) --
	( 83.42,531.73) --
	( 96.59,531.73) --
	( 96.59,531.32) --
	(109.77,531.32) --
	(109.77,530.81) --
	(122.95,530.81) --
	(122.95,530.21) --
	(136.12,530.21) --
	(136.12,529.54) --
	(149.30,529.54) --
	(149.30,528.76) --
	(162.48,528.76) --
	(162.48,527.90) --
	(175.66,527.90) --
	(175.66,526.95) --
	(188.83,526.95) --
	(188.83,525.91) --
	(202.01,525.91) --
	(202.01,524.81) --
	(215.19,524.81) --
	(215.19,523.61) --
	(228.36,523.61) --
	(228.36,522.37) --
	(241.54,522.37) --
	(241.54,521.03) --
	(254.72,521.03) --
	(254.72,519.61) --
	(267.89,519.61) --
	(267.89,518.13) --
	(281.07,518.13) --
	(281.07,516.58) --
	(294.25,516.58) --
	(294.25,514.97);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.24) --
	( 70.24,532.24) --
	( 70.24,531.95) --
	( 83.42,531.95) --
	( 83.42,531.52) --
	( 96.59,531.52) --
	( 96.59,530.99) --
	(109.77,530.99) --
	(109.77,530.36) --
	(122.95,530.36) --
	(122.95,529.62) --
	(136.12,529.62) --
	(136.12,528.78) --
	(149.30,528.78) --
	(149.30,527.83) --
	(162.48,527.83) --
	(162.48,526.76) --
	(175.66,526.76) --
	(175.66,525.59) --
	(188.83,525.59) --
	(188.83,524.34) --
	(202.01,524.34) --
	(202.01,523.00) --
	(215.19,523.00) --
	(215.19,521.57) --
	(228.36,521.57) --
	(228.36,520.03) --
	(241.54,520.03) --
	(241.54,518.38) --
	(254.72,518.38) --
	(254.72,516.64) --
	(267.89,516.64) --
	(267.89,514.79) --
	(281.07,514.79) --
	(281.07,512.92) --
	(294.25,512.92) --
	(294.25,511.00);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,531.51) --
	( 70.24,531.51) --
	( 70.24,530.38) --
	( 83.42,530.38) --
	( 83.42,529.04) --
	( 96.59,529.04) --
	( 96.59,527.67) --
	(109.77,527.67) --
	(109.77,526.22) --
	(122.95,526.22) --
	(122.95,524.74) --
	(136.12,524.74) --
	(136.12,523.26) --
	(149.30,523.26) --
	(149.30,521.73) --
	(162.48,521.73) --
	(162.48,520.19) --
	(175.66,520.19) --
	(175.66,518.63) --
	(188.83,518.63) --
	(188.83,517.08) --
	(202.01,517.08) --
	(202.01,515.54) --
	(215.19,515.54) --
	(215.19,514.00) --
	(228.36,514.00) --
	(228.36,512.49) --
	(241.54,512.49) --
	(241.54,510.97) --
	(254.72,510.97) --
	(254.72,509.45) --
	(267.89,509.45) --
	(267.89,507.96) --
	(281.07,507.96) --
	(281.07,506.46) --
	(294.25,506.46) --
	(294.25,504.92);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,531.12) --
	( 70.24,531.12) --
	( 70.24,529.67) --
	( 83.42,529.67) --
	( 83.42,527.97) --
	( 96.59,527.97) --
	( 96.59,526.22) --
	(109.77,526.22) --
	(109.77,524.43) --
	(122.95,524.43) --
	(122.95,522.60) --
	(136.12,522.60) --
	(136.12,520.76) --
	(149.30,520.76) --
	(149.30,518.89) --
	(162.48,518.89) --
	(162.48,517.00) --
	(175.66,517.00) --
	(175.66,515.09) --
	(188.83,515.09) --
	(188.83,513.22) --
	(202.01,513.22) --
	(202.01,511.38) --
	(215.19,511.38) --
	(215.19,509.55) --
	(228.36,509.55) --
	(228.36,507.70) --
	(241.54,507.70) --
	(241.54,505.84) --
	(254.72,505.84) --
	(254.72,504.00) --
	(267.89,504.00) --
	(267.89,502.15) --
	(281.07,502.15) --
	(281.07,500.38) --
	(294.25,500.38) --
	(294.25,498.55);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.82) --
	( 70.24,436.82) --
	( 70.24,436.59) --
	( 83.42,436.59) --
	( 83.42,436.27) --
	( 96.59,436.27) --
	( 96.59,435.85) --
	(109.77,435.85) --
	(109.77,435.33) --
	(122.95,435.33) --
	(122.95,434.71) --
	(136.12,434.71) --
	(136.12,434.01) --
	(149.30,434.01) --
	(149.30,433.22) --
	(162.48,433.22) --
	(162.48,432.33) --
	(175.66,432.33) --
	(175.66,431.35) --
	(188.83,431.35) --
	(188.83,430.30) --
	(202.01,430.30) --
	(202.01,429.17) --
	(215.19,429.17) --
	(215.19,427.95) --
	(228.36,427.95) --
	(228.36,426.66) --
	(241.54,426.66) --
	(241.54,425.30) --
	(254.72,425.30) --
	(254.72,423.86) --
	(267.89,423.86) --
	(267.89,422.34) --
	(281.07,422.34) --
	(281.07,420.76) --
	(294.25,420.76) --
	(294.25,419.13);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.79) --
	( 70.24,436.79) --
	( 70.24,436.50) --
	( 83.42,436.50) --
	( 83.42,436.07) --
	( 96.59,436.07) --
	( 96.59,435.53) --
	(109.77,435.53) --
	(109.77,434.89) --
	(122.95,434.89) --
	(122.95,434.16) --
	(136.12,434.16) --
	(136.12,433.29) --
	(149.30,433.29) --
	(149.30,432.32) --
	(162.48,432.32) --
	(162.48,431.20) --
	(175.66,431.20) --
	(175.66,429.97) --
	(188.83,429.97) --
	(188.83,428.71) --
	(202.01,428.71) --
	(202.01,427.33) --
	(215.19,427.33) --
	(215.19,425.87) --
	(228.36,425.87) --
	(228.36,424.24) --
	(241.54,424.24) --
	(241.54,422.48) --
	(254.72,422.48) --
	(254.72,420.67) --
	(267.89,420.67) --
	(267.89,418.79) --
	(281.07,418.79) --
	(281.07,416.82) --
	(294.25,416.82) --
	(294.25,414.88);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.03) --
	( 70.24,436.03) --
	( 70.24,434.88) --
	( 83.42,434.88) --
	( 83.42,433.58) --
	( 96.59,433.58) --
	( 96.59,432.19) --
	(109.77,432.19) --
	(109.77,430.73) --
	(122.95,430.73) --
	(122.95,429.19) --
	(136.12,429.19) --
	(136.12,427.66) --
	(149.30,427.66) --
	(149.30,426.11) --
	(162.48,426.11) --
	(162.48,424.54) --
	(175.66,424.54) --
	(175.66,422.95) --
	(188.83,422.95) --
	(188.83,421.38) --
	(202.01,421.38) --
	(202.01,419.81) --
	(215.19,419.81) --
	(215.19,418.25) --
	(228.36,418.25) --
	(228.36,416.70) --
	(241.54,416.70) --
	(241.54,415.15) --
	(254.72,415.15) --
	(254.72,413.61) --
	(267.89,413.61) --
	(267.89,412.08) --
	(281.07,412.08) --
	(281.07,410.56) --
	(294.25,410.56) --
	(294.25,409.00);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,435.82) --
	( 70.24,435.82) --
	( 70.24,434.36) --
	( 83.42,434.36) --
	( 83.42,432.67) --
	( 96.59,432.67) --
	( 96.59,430.87) --
	(109.77,430.87) --
	(109.77,429.08) --
	(122.95,429.08) --
	(122.95,427.28) --
	(136.12,427.28) --
	(136.12,425.38) --
	(149.30,425.38) --
	(149.30,423.49) --
	(162.48,423.49) --
	(162.48,421.50) --
	(175.66,421.50) --
	(175.66,419.53) --
	(188.83,419.53) --
	(188.83,417.65) --
	(202.01,417.65) --
	(202.01,415.76) --
	(215.19,415.76) --
	(215.19,413.91) --
	(228.36,413.91) --
	(228.36,411.95) --
	(241.54,411.95) --
	(241.54,409.99) --
	(254.72,409.99) --
	(254.72,408.06) --
	(267.89,408.06) --
	(267.89,406.19) --
	(281.07,406.19) --
	(281.07,404.32) --
	(294.25,404.32) --
	(294.25,402.48);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.35) --
	( 70.24,341.35) --
	( 70.24,341.12) --
	( 83.42,341.12) --
	( 83.42,340.80) --
	( 96.59,340.80) --
	( 96.59,340.38) --
	(109.77,340.38) --
	(109.77,339.87) --
	(122.95,339.87) --
	(122.95,339.28) --
	(136.12,339.28) --
	(136.12,338.61) --
	(149.30,338.61) --
	(149.30,337.84) --
	(162.48,337.84) --
	(162.48,336.98) --
	(175.66,336.98) --
	(175.66,336.03) --
	(188.83,336.03) --
	(188.83,335.00) --
	(202.01,335.00) --
	(202.01,333.89) --
	(215.19,333.89) --
	(215.19,332.70) --
	(228.36,332.70) --
	(228.36,331.45) --
	(241.54,331.45) --
	(241.54,330.12) --
	(254.72,330.12) --
	(254.72,328.70) --
	(267.89,328.70) --
	(267.89,327.22) --
	(281.07,327.22) --
	(281.07,325.67) --
	(294.25,325.67) --
	(294.25,324.06);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,341.30) --
	( 70.24,341.30) --
	( 70.24,341.00) --
	( 83.42,341.00) --
	( 83.42,340.57) --
	( 96.59,340.57) --
	( 96.59,340.03) --
	(109.77,340.03) --
	(109.77,339.38) --
	(122.95,339.38) --
	(122.95,338.61) --
	(136.12,338.61) --
	(136.12,337.76) --
	(149.30,337.76) --
	(149.30,336.78) --
	(162.48,336.78) --
	(162.48,335.71) --
	(175.66,335.71) --
	(175.66,334.51) --
	(188.83,334.51) --
	(188.83,333.23) --
	(202.01,333.23) --
	(202.01,331.82) --
	(215.19,331.82) --
	(215.19,330.32) --
	(228.36,330.32) --
	(228.36,328.73) --
	(241.54,328.73) --
	(241.54,327.07) --
	(254.72,327.07) --
	(254.72,325.34) --
	(267.89,325.34) --
	(267.89,323.47) --
	(281.07,323.47) --
	(281.07,321.56) --
	(294.25,321.56) --
	(294.25,319.55);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,340.55) --
	( 70.24,340.55) --
	( 70.24,339.42) --
	( 83.42,339.42) --
	( 83.42,338.11) --
	( 96.59,338.11) --
	( 96.59,336.75) --
	(109.77,336.75) --
	(109.77,335.30) --
	(122.95,335.30) --
	(122.95,333.82) --
	(136.12,333.82) --
	(136.12,332.35) --
	(149.30,332.35) --
	(149.30,330.83) --
	(162.48,330.83) --
	(162.48,329.30) --
	(175.66,329.30) --
	(175.66,327.75) --
	(188.83,327.75) --
	(188.83,326.20) --
	(202.01,326.20) --
	(202.01,324.66) --
	(215.19,324.66) --
	(215.19,323.12) --
	(228.36,323.12) --
	(228.36,321.61) --
	(241.54,321.61) --
	(241.54,320.09) --
	(254.72,320.09) --
	(254.72,318.58) --
	(267.89,318.58) --
	(267.89,317.08) --
	(281.07,317.08) --
	(281.07,315.59) --
	(294.25,315.59) --
	(294.25,314.04);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,341.49) --
	( 57.06,341.49) --
	( 57.06,340.23) --
	( 70.24,340.23) --
	( 70.24,338.73) --
	( 83.42,338.73) --
	( 83.42,337.01) --
	( 96.59,337.01) --
	( 96.59,335.22) --
	(109.77,335.22) --
	(109.77,333.37) --
	(122.95,333.37) --
	(122.95,331.48) --
	(136.12,331.48) --
	(136.12,329.61) --
	(149.30,329.61) --
	(149.30,327.68) --
	(162.48,327.68) --
	(162.48,325.78) --
	(175.66,325.78) --
	(175.66,323.83) --
	(188.83,323.83) --
	(188.83,321.93) --
	(202.01,321.93) --
	(202.01,319.98) --
	(215.19,319.98) --
	(215.19,318.06) --
	(228.36,318.06) --
	(228.36,316.16) --
	(241.54,316.16) --
	(241.54,314.28) --
	(254.72,314.28) --
	(254.72,312.45) --
	(267.89,312.45) --
	(267.89,310.59) --
	(281.07,310.59) --
	(281.07,308.77) --
	(294.25,308.77) --
	(294.25,306.87);
\definecolor{drawColor}{gray}{0.20}

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,245.72) --
	( 70.24,245.72) --
	( 70.24,245.22) --
	( 83.42,245.22) --
	( 83.42,244.49) --
	( 96.59,244.49) --
	( 96.59,243.55) --
	(109.77,243.55) --
	(109.77,242.36) --
	(122.95,242.36) --
	(122.95,240.98) --
	(136.12,240.98) --
	(136.12,239.40) --
	(149.30,239.40) --
	(149.30,237.63) --
	(162.48,237.63) --
	(162.48,235.66) --
	(175.66,235.66) --
	(175.66,233.45) --
	(188.83,233.45) --
	(188.83,231.09) --
	(202.01,231.09) --
	(202.01,228.56) --
	(215.19,228.56) --
	(215.19,225.87) --
	(228.36,225.87) --
	(228.36,223.01) --
	(241.54,223.01) --
	(241.54,219.97) --
	(254.72,219.97) --
	(254.72,216.86) --
	(267.89,216.86) --
	(267.89,213.57) --
	(281.07,213.57) --
	(281.07,210.22) --
	(294.25,210.22) --
	(294.25,206.69);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,246.02) --
	( 57.06,246.02) --
	( 57.06,245.59) --
	( 70.24,245.59) --
	( 70.24,244.91) --
	( 83.42,244.91) --
	( 83.42,243.97) --
	( 96.59,243.97) --
	( 96.59,242.78) --
	(109.77,242.78) --
	(109.77,241.36) --
	(122.95,241.36) --
	(122.95,239.66) --
	(136.12,239.66) --
	(136.12,237.77) --
	(149.30,237.77) --
	(149.30,235.63) --
	(162.48,235.63) --
	(162.48,233.29) --
	(175.66,233.29) --
	(175.66,230.69) --
	(188.83,230.69) --
	(188.83,227.85) --
	(202.01,227.85) --
	(202.01,224.84) --
	(215.19,224.84) --
	(215.19,221.67) --
	(228.36,221.67) --
	(228.36,218.22) --
	(241.54,218.22) --
	(241.54,214.58) --
	(254.72,214.58) --
	(254.72,210.76) --
	(267.89,210.76) --
	(267.89,206.94) --
	(281.07,206.94) --
	(281.07,202.93) --
	(294.25,202.93) --
	(294.25,199.00);
\definecolor{drawColor}{RGB}{248,118,109}
